Incentivizing Exploration with Unbiased History

### 2018-10-09 llevel.tex
add a proof for Cor 6.4

Our recommendation policy has $L$ levels and two types of groups: $G$-groups and $\Gamma$-groups. Each level has $S^2$ $G$-groups for $S = 2^{10}\log(T)$. Label the $G$-groups in the $l$-th level as $G_{l,u,v}$ for $u,v \in [S]$. Level $2$ to level $L$ also have $S^2$ $\Gamma$-groups. Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [S]$.

We set the group size as following. For $l < L$,
\[
T_l = T^{\frac{2^{L-1} + 2^{L-2} + \cdots + 2^{L-l}}{2^{L-1}+ 2^{L-2} + \cdots + 1}}/S^3.
\]
and 
\[
T_L = (T - T_1 \cdot \GdT\cdot S^2 - (T_2 + \cdots + T_{l-1}) S^3) /S^3
\]
We restrict $L$ to be at most $\log(\ln(T)/\log(S^4))$ so that $T_l / T_{l-1} \geq T^{1/2^L} \geq S^4$ for $l = 2,...,L-1$. $T_L$ is a little bit different because we want total number of agents to be $T$.

Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel. For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (S-1)$ agents in group $\Gamma_{l,u,v}$.

@@

\begin{theorem}
The $L$-level recommendation policy gets expected regret $O\left(T^{\frac{2^{L-1}}{2^L-1}} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(10S^3))$. In particular, if we pick $L = \log(\ln(T)/\log(10S^3))$, the expected regret is at most $O(T^{1/2} \log^5(T))$. 
\end{theorem}

\begin{proof}
Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. Similarly as the proof of Theorem \ref{thm:3level}, we start with some clean events.

\begin{itemize}
\item For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level. By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ For group $G_{1,u,v}$, define $W_1^{a,u,v}$ to be the event that the number of arm $a$ pulls in this group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,u,v}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,u,v}W_1^{a,u,v}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S^2}{T^2}.
\]

\item For each agent $t$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in agent $t$'s observed history pull arm $a$.  Define $W_2^{t,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{3\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound, 
\[
\Pr[W_2^{t,a,t_1,t_2}] \geq 1 - 2\exp(-6\log(T)) \geq 1- 2/T^6.
\]

@@

\item For $2\leq l \leq L-1$, $u\in [S]$ and each arm $a$, define $n^{l,u,a}$ to be the number of arm $a$ pulls in groups $G_{l,u,1},...,G_{l,u,S}$. Define $W_3^{l,u,a,high}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at least $\mu_a + 1/\sqrt{n^{l,u,a}}$. Define $W_3^{l,u,a,low}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at most $\mu_a - 1/\sqrt{n^{l,u,a}}$.

@@

\item For first-level groups $G_{1,u,1},...,G_{1,u,S}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$. Define $W_4^{u,a,high}$  to be the event that first $q_a T_1 S$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1 S}$ and define $W_4^{u,a,low}$  to be the event that first $q_a T_1S$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1S }$. By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_4^{u,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1S}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{u,a,low}] > 1/4.
\]
Since $W_4^{u,a,high}$ is independent with $W_4^{u,3-a,low}$, we have
\[
\Pr[W_4^{u,a,high} \cap W_4^{u,3-a,low}] =\Pr[W_4^{u,a,high}] \cdot  \Pr[W_4^{u,3-a,low}]>(1/4)^2 = 1/16.
\]
Now define $W^{a}_4$ as $\bigcup_u (W_4^{u,a,high} \cap W_4^{u,3-a,low})$. Notice that $(W_4^{u,a,high} \cap W_4^{u,3-a,low})$ are independent across different $u$'s. So we have
\[
\Pr[W^{a}_4] \geq 1- (1-1/16)^S \geq 1 -1/T^2.
\]
Finally we define $W_4$ as $\bigcap_{a} W^{a}_4$. By union bound,
\[
\Pr[W_4] \geq 1- 2/T^2.
\]
\end{itemize}

@@

We prove the above via induction on $l$. %For notation convenience, define $\bar{\mu}^{l,u}_a$  to be the empirical mean of arm $a$ pulls in the history observed by agents in groups $G_{l,1,u},...,G_{l,S,u}$ and $\Gamma_{l,1,u},...,\Gamma_{l,S,u}$ (they observe the same history).
We start by the base case when $l=2$. For each arm $a$, $W_4$ implies there exists $u_a$ such that $W^{u_a,a,high}_4$ and $W^{u_a,3-a,low}_4$ happen. For an agent $t$  in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$.
$W_4^{u_a,a,high}$,  $W_1^{a,u_a,v}$ and $W_2$ together imply that 
\begin{align*}
\bar{\mu}_a ^t &\geq \mu_a + \left(q_aT_1S \cdot \frac{1}{\sqrt{q_aT_1S}} - \GdT \sqrt{T_1\log(T)} S\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}S}} \right) \cdot \frac{1}{(q_a T_1+ \GdT \sqrt{T_1\log(T)})S} \\
&> \mu_a + \frac{1}{4\sqrt{q_aT_1S}}.
\end{align*}
The second last inequality holds when $T$ larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1S}}.
\]
Then we have
\begin{align*}
\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}\\
&\geq -\varepsilon_1+ \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}\\
&\geq \frac{1}{8\sqrt{q_aT_1S}} + \frac{1}{8\sqrt{q_{3-a} T_1S}}.
\end{align*}
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{q_aT_1S/2}} - \frac{c_m}{\sqrt{q_{3-a} T_1S/2}}\\
&> \frac{1}{8\sqrt{q_aT_1S}} + \frac{1}{8\sqrt{q_{3-a} T_1S}} -   \frac{c_m}{\sqrt{q_aT_1S/2}} - \frac{c_m}{\sqrt{q_{3-a} T_1S/2}}\\
&>0.
\end{align*}
The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}. Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$ all pull arm $a$.

@@

\begin{claim}
\label{clm:l2_exploit}
For any $2 \leq l \leq L$, if $\varepsilon_{l-1} S < \mu_1 - \mu_2 < \varepsilon_{l-2} S$, there are no pulls of arm 2 in groups with level $l,...,L$. 
\end{claim}

@@

By Claim \ref{clm:l2_exploit}, we know that the expected regret conditioned the intersection of clean events is at most 
\begin{align*}
&\max\left( T_1T_GS^2 , \max_{l \geq 2} \varepsilon_{l-1}S(T_1T_GS^2 + T_2 S^3 + \cdots + T_lS^3)\right) \\
\leq & \max\left( T_1T_GS^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l S^4 \right)\\
= &O(T^{\frac{2^{L-1}}{2^L-1}} \log^2(T)).
\end{align*}
\end{proof}

Now we are going to change the parameters of the $L$-level recommendation policy a little bit and prove the below corollary. We will keep $S$ the same (i.e. $S = 2^{10}\log(T)$). We are going to change $L$ and $T_1,...,T_L$. We set $L = \log(T)/\log(10S^3)$, $T_l = (10S^3)^l$ for $l=1,...,L-1$ and $T_L = (T - T_1 \GdT S^2 - S^3\sum_{l=2}^{L-1} T_l)/S^3$.  
\begin{corollary}
With the proper setting of $L$ and $T_1,...,T_L$ discribed above, the $L$-level recommendation policy gets expected regret $O(polylog(T) /\Delta)$. Here $\Delta = \mu_1 -\mu_2$ and the $L$-level recommendation policy does not need to know $\Delta$ ahead of the time. Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{corollary}

\begin{proof}
\end{proof}

>>>>

Our recommendation policy has $L$ levels and two types of groups: $G$-groups and $\Gamma$-groups. Each level has $S^2$ $G$-groups for $S = 2^{10}\log(T)$. Label the $G$-groups in the $l$-th level as $G_{l,u,v}$ for $u,v \in [S]$. Level $2$ to level $L$ also have $S^2$ $\Gamma$-groups. Label the $\Gamma$-groups in the $l$-th level as $\Gamma_{l,u,v}$ for $u,v \in [S]$. Each first-level group ($G_{1,u,v}$ for $u,v\in [S]$) has $T_1$ \ALGG of $\GdT$ rounds in parallel. For $l \geq 2$, there are $T_l$ agents in group $G_{l,u,v}$ and there are $T_l (S-1)$ agents in group $\Gamma_{l,u,v}$. We will pick $T_1,...,T_L$ in the proof of Theorem \ref{thm:llevel}.

@@

\begin{theorem}
\label{thm:llevel}
The $L$-level recommendation policy gets expected regret $O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right)$ for $L \leq \log(\ln(T)/\log(S^4))$. In particular, if we pick $L = \log(\ln(T)/\log(S^4))$, the expected regret is $O(T^{1/2} polylog(T))$. 
\end{theorem}

\begin{proof}
Wlog we assume $\mu_1 \geq \mu_2$ as the recommendation policy is symmetric to both arms. We will set $T_l$'s later in the proof. Before that, we are only going to assume $T_l / T_{l-1} \geq S^4$ for $l=2,...,L-1$ and $T_1 \geq S^4$.

Similarly as the proof of Theorem \ref{thm:3level}, we start with some clean events.

\begin{itemize}
\item  \textbf{Concentration of the number of arm $a$ pulls in the first level:}

For $a \in \{1,2\}$, define $q_a$ to be the expected number of arm $a$ pulls in one run of \ALGG used in the first level. By Lemma \ref{lem:greedy}, we know $\GdP \leq q_a \leq \GdT$ For group $G_{1,u,v}$, define $W_1^{a,u,v}$ to be the event that the number of arm $a$ pulls in this group is between $q_a T_1- \GdT \sqrt{T_1\log(T)}$ and $q_a T_1 + \GdT \sqrt{T_1\log(T)}$. By Chernoff bound,
\[
\Pr[W_1^{a,u,v}] \geq 1-2\exp(-2\log(T)) \geq 1-2/T^2.
\]
Define $W_1$ to be the intersection of all these events (i.e. $W_1 = \bigcap_{a,u,v}W_1^{a,u,v}$). By union bound, we have
\[
\Pr[W_1] \geq 1- \frac{4S^2}{T^2}.
\]

\item \textbf{Concentration of the empirical mean of arm $a$ pulls in the history observed by agent $t$:}

 For each agent $t$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in agent $t$'s observed history pull arm $a$.  Define $W_2^{t,a,t_1,t_2}$ to be the event that the mean of $t_1$-th to $t_2$-th pulls in the tape is at most $\sqrt{\frac{3\log(T)}{t_2-t_1+1}}$ away from $\mu_a$. By Chernoff bound, 
\[
\Pr[W_2^{t,a,t_1,t_2}] \geq 1 - 2\exp(-6\log(T)) \geq 1- 2/T^6.
\]

@@

\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the $l$-th level  for $l \geq 2$:}

For $2\leq l \leq L-1$, $u\in [S]$ and each arm $a$, define $n^{l,u,a}$ to be the number of arm $a$ pulls in groups $G_{l,u,1},...,G_{l,u,S}$. Define $W_3^{l,u,a,high}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at least $\mu_a + 1/\sqrt{n^{l,u,a}}$. Define $W_3^{l,u,a,low}$ as the event that $n^{l,u,a} \geq T_l$ implies the empirical mean of arm $a$ pulls in group $G_{l,u,1},...,G_{l,u,S}$ is at most $\mu_a - 1/\sqrt{n^{l,u,a}}$.

@@

\item \textbf{Anti-concentration of the empirical mean of arm $a$ pulls in the first level:}

For first-level groups $G_{1,u,1},...,G_{1,u,S}$ and arm $a$, imagine there is a tape of enough arm $a$ pulls sampled before the recommendation policy starts and these samples are revealed one by one whenever agents in these groups pull arm $a$. Define $W_4^{u,a,high}$  to be the event that first $q_a T_1 S$ pulls of arm $a$ in the tape has empirical mean at least $\mu_a + 1/\sqrt{q_a T_1 S}$ and define $W_4^{u,a,low}$  to be the event that first $q_a T_1S$ pulls of arm $a$ in the tape has empirical mean at most $\mu_a - 1/\sqrt{q_a T_1S }$. By Berry-Essen Theorem and $\mu_a \in [1/3,2/3]$, we have
\[
\Pr[W_4^{u,a,high}] \geq (1-\Phi(1/2)) - \frac{5}{\sqrt{q_aT_1S}} > 1/4.
\]
The last inequality follows when $T$ is larger than some constant.
Similarly we also have 
\[
\Pr[W_4^{u,a,low}] > 1/4.
\]
Since $W_4^{u,a,high}$ is independent with $W_4^{u,3-a,low}$, we have
\[
\Pr[W_4^{u,a,high} \cap W_4^{u,3-a,low}] =\Pr[W_4^{u,a,high}] \cdot  \Pr[W_4^{u,3-a,low}]>(1/4)^2 = 1/16.
\]
Now define $W^{a}_4$ as $\bigcup_u (W_4^{u,a,high} \cap W_4^{u,3-a,low})$. Notice that $(W_4^{u,a,high} \cap W_4^{u,3-a,low})$ are independent across different $u$'s. So we have
\[
\Pr[W^{a}_4] \geq 1- (1-1/16)^S \geq 1 -1/T^2.
\]
Finally we define $W_4$ as $\bigcap_{a} W^{a}_4$. By union bound,
\[
\Pr[W_4] \geq 1- 2/T^2.
\]
\end{itemize}

@@

We prove the above via induction on $l$. %For notation convenience, define $\bar{\mu}^{l,u}_a$  to be the empirical mean of arm $a$ pulls in the history observed by agents in groups $G_{l,1,u},...,G_{l,S,u}$ and $\Gamma_{l,1,u},...,\Gamma_{l,S,u}$ (they observe the same history).
We start by the base case when $l=2$. For each arm $a$, $W_4$ implies there exists $u_a$ such that $W^{u_a,a,high}_4$ and $W^{u_a,3-a,low}_4$ happen. For an agent $t$  in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$.
$W_4^{u_a,a,high}$,  $W_1^{a,u_a,v}$ and $W_2$ together imply that 
\begin{align*}
\bar{\mu}_a ^t &\geq \mu_a + \left(q_aT_1S \cdot \frac{1}{\sqrt{q_aT_1S}} - \GdT \sqrt{T_1\log(T)} S\cdot \sqrt{\frac{3\log(T)}{ \GdT \sqrt{T_1\log(T)}S}} \right) \cdot \frac{1}{(q_a T_1+ \GdT \sqrt{T_1\log(T)})S} \\
&> \mu_a + \frac{1}{4\sqrt{q_aT_1S}}.
\end{align*}
The second last inequality holds when $T$ is larger than some constant.
Similarly, we also have
\[
\bar{\mu}_{3-a}^t< \mu_{3-a}   - \frac{1}{4\sqrt{q_{3-a} T_1S}}.
\]
Then we have
\begin{align*}
\bar{\mu}^t_a - \bar{\mu}^t_{3-a} &> \mu_a - \mu_{3-a} + \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}\\
&\geq -\varepsilon_1+ \frac{1}{4\sqrt{q_aT_1S}} + \frac{1}{4\sqrt{q_{3-a} T_1S}}\\
&\geq \frac{1}{8\sqrt{q_aT_1S}} + \frac{1}{8\sqrt{q_{3-a} T_1S}}.
\end{align*}
By Assumption \ref{ass:embehave}, we have
\begin{align*}
\hat{\mu}_a^t - \hat{\mu}_{3-a}^t &> \bar{\mu}^t_a - \bar{\mu}^t_{3-a} -  \frac{c_m}{\sqrt{q_aT_1S/2}} - \frac{c_m}{\sqrt{q_{3-a} T_1S/2}}\\
&> \frac{1}{8\sqrt{q_aT_1S}} + \frac{1}{8\sqrt{q_{3-a} T_1S}} -   \frac{c_m}{\sqrt{q_aT_1S/2}} - \frac{c_m}{\sqrt{q_{3-a} T_1S/2}}\\
&>0.
\end{align*}
The last inequality holds since $c_m$ is a small enough constant defined in Assumption \ref{ass:embehave}. Therefore we know agents in groups $G_{2,1,u_a},...,G_{2,S,u_a}$ and $\Gamma_{2,1,u_a},...,\Gamma_{2,S,u_a}$ all pull arm $a$.

@@

\begin{claim}
\label{clm:l2_exploit}
For any $2 \leq l \leq L$, if $\varepsilon_{l-1} S\leq \mu_1 - \mu_2 < \varepsilon_{l-2} S$, there are no pulls of arm 2 in groups with level $l,...,L$. 
\end{claim}

@@

Now we set the group sizes $T_l$'s as following. For $l < L$,
\[
T_l = T^{\frac{2^{L-1} + 2^{L-2} + \cdots + 2^{L-l}}{2^{L-1}+ 2^{L-2} + \cdots + 1}}/S^3.
\]
and 
\[
T_L = (T - T_1 \cdot \GdT\cdot S^2 - (T_2 + \cdots + T_{l-1}) S^3) /S^3
\]
We restrict $L$ to be at most $\log(\ln(T)/\log(S^4))$ so that $T_l / T_{l-1} \geq T^{1/2^L} \geq S^4$ for $l = 2,...,L-1$. $T_L$ is a little bit different because we want total number of agents to be $T$.

By Claim \ref{clm:l2_exploit}, we know that the expected regret conditioned the intersection of clean events is at most 
\begin{align*}
&\max\left( T_1T_GS^2 , \max_{l \geq 2} \varepsilon_{l-1}S(T_1T_GS^2 + T_2 S^3 + \cdots + T_lS^3)\right) \\
\leq & \max\left( T_1T_GS^2 , \max_{l \geq 2} 2 \varepsilon_{l-1} T_l S^4 \right)\\
= &O\left(T^{2^{L-1}/(2^L-1)} \log^2(T) \right).
\end{align*}
\end{proof}

Now we are going to change the parameters of the $L$-level recommendation policy a little bit and prove the below corollary. We will keep $S$ the same (i.e. $S = 2^{10}\log(T)$). We are going to change $L$ and $T_1,...,T_L$. We set $L = \log(T)/\log(S^4)$, $T_l = (S^4)^l$ for $l=1,...,L-1$ and $T_L = (T - T_1 \GdT S^2 - S^3\sum_{l=2}^{L-1} T_l)/S^3$.  
\begin{corollary}
With the proper setting of $L$ and $T_1,...,T_L$ described above, the $L$-level recommendation policy gets expected regret $O(\min(polylog(T) /\Delta,  T\Delta))$. Here $\Delta = \mu_1 -\mu_2$ and the $L$-level recommendation policy does not need to know $\Delta$. Moreover, agent $t$ observes a subhistory of size at least $\Omega( \lfloor t/polylog(T)\rfloor)$. 
\end{corollary}

\begin{proof}
Notice that in the proof of Theorem \ref{thm:llevel}, by the end of Claim \ref{clm:l2_exploit}, the only constraint we need about $T_l$'s is that $T_l / T_{l-1} \geq S^4$ for $l=2,...,L-1$ and $T_1 \geq S^4$. And our new settings of $T_l$'s still satisfy this constraint. So we can reuse the proof of Theorem \ref{thm:llevel} till the end of Claim \ref{clm:l2_exploit}.

First of all, notice that even always picking the sub-optimal arm gives expected regret $T(\mu_1-\mu_2) = T\Delta$. In the rest of the proof, we just need to show the expected regret is $O(polylog(T)/\Delta)$. Now consider two cases:
\begin{itemize}
\item $\Delta < \varepsilon_{L-1} S$. In this case, we know $T\Delta = O(polylog(T)/\Delta)$. So the expected regret is $O(T\Delta) = O(polylog(T) /\Delta)$.
\item $\Delta \geq \varepsilon_{L-1} S$. In this case, we can find $l \in \{2,...,L\}$ such that $\varepsilon_{l-1} S\leq \Delta < \varepsilon_{l-2} S$. By Claim \ref{clm:l2_exploit}, we can bound the expected regret by
\begin{align*}
&\Delta \cdot (T_1 \GdT S^2  +T_2 S^3+ \cdots T_{l-1} S^3)\\
=& O(\Delta T_{l-1}S^3) \\
=&O(\Delta T_{l-2}S^7) \\
=&O(\Delta\cdot  \frac{1}{\varepsilon^2_{l-2}}\cdot S^6)\\
=&O(\Delta \cdot \frac{1}{\Delta^2}\cdot S^8)\\
=&O(polylog(T)/\Delta).
\end{align*}
\end{itemize}
\end{proof}
